### 2008-03-17 SAiP/Module1/H3/doc/architecturaldesign.tex
Adding last part about C&C structures

\begin{itemize}
  \item Process or communicating processes.
	\begin{itemize}
	  \item This structure shows the execution path through a system, and is used to give the engineer an understand about the dynamic behaviour of the system. These structures may help ingeneers increase Performance and Availability.
	\end{itemize}
  \item Concurrency.
	\begin{itemize}
	  \item This structure is used to see the parallelism in the system, or part of the system, and when a system, or part of a system, is build around this structure it promotes performance. 
	\end{itemize}
  \item Shared data or Repository
	\begin{itemize}
	  \item This is a very good structure to use to illustarte how the data is processed and consumed to/from the database (Database Facade). When a system, or part of a system, is build around this structure it promotes performance and data entegrity. 
	\end{itemize}
  \item Client-server
	\begin{itemize}
  		\item This is a very good structure to see the protocols used between the clients and the server, and the messages they communicate. When a system, or part of a system, is build around this structure it promotes seperation of concern (i.e. Modifiability) and allows for Availability tactics like Load balancing.
	\end{itemize}
\end{itemize}

\fixme{Insert diagrams for C&C}

>>>>

\begin{itemize}
  \item Process or communicating processes.
	\begin{itemize}
	  \item This structure shows the execution path through a system, and is used to give the engineer an understand about the dynamic behaviour of the system. These structures may help engineers increase Performance and Availability.
	\end{itemize}
  \item Concurrency.
	\begin{itemize}
	  \item This structure is used to see the parallelism in the system, or part of the system, and when a system, or part of a system, is build around this structure it promotes performance. 
	\end{itemize}
  \item Shared data or Repository
	\begin{itemize}
	  \item This is a very good structure to use to illustarte how the data is processed and consumed to/from the database (Server to/from Database Facade). When a system, or part of a system, is build around this structure it promotes performance and data entegrity. 
	\end{itemize}
  \item Client-server
	\begin{itemize}
  		\item This is a very good structure to see the protocols used between the Clients and the Server, and the messages they communicate. When a system, or part of a system, is build around this structure it promotes seperation of concern (i.e. Modifiability) and allows for Availability tactics like Load balancing.
	\end{itemize}
\end{itemize}

In the Beer Web Store has two clear C\&C structures, the Shared data structure between the Server and the Database Facade and the Client-server between the Client and Server (see Figure \ref{fig:module_view}).

The Process or Communicating processes is a more fine-grained structure, and an example of this may be seen in Figure \ref{fig:ad_sequence}.

The Concurrency structure is not used in the overall elements, yet may be employed in a given element to achieve more performance.

\fixme{Possible extention - insert diagrams}
